INGOs and instrumental factors

### 2023-05-10 notebook/desc-work.qmd
Add obstacles + rename

---
title: "Descriptive stuff"
format:
  html:
    code-fold: true
---

@@

```{r tab-activities-contentiousness-diffs}
#| tbl-cap: Median differences in proportion of high and low contention INGOs selecting frequency of type of work. Probability that the proportion is greater than 0 given in parentheses.
models_activities %>% 
  unnest(diffs_summary) %>% 
  mutate(nice_value = glue::glue(
    "{diff}<br>({p})",
    diff = label_number(style_negative = "minus", accuracy = 0.01)(y),
    p = label_number(accuracy = 0.01)(p_greater_0))
  ) %>% 
  ungroup() %>% 
  select(question, response, nice_value) %>% 
  pivot_wider(names_from = "response", values_from = "nice_value") %>% 
  gt() %>%
  fmt_markdown(columns = 2:4) %>%
  cols_align(align = "left", columns = question) %>%
  cols_label(question = "") %>% 
  opts_theme()
```

@@

```{r analyze-obstacles}
# df.plot.obstacles.raw <- survey.orgs.clean %>%
#   filter(!is.na(Q3.12_obstacle)) %>%
#   mutate(obstacle = str_split(Q3.12_obstacle, ", ")) %>%
#   unnest(obstacle) %>%
#   mutate(obstacle = recode(obstacle,
#     `access to country` = "bureaucratic, legal, and political",
#     `political context` = "bureaucratic, legal, and political",
#     `bureaucratic and legal` = "bureaucratic, legal, and political"
#   )) %>%
#   group_by(obstacle) %>%
#   summarise(num = n()) %>%
#   arrange(desc(num))
# 
# df.plot.obstacles.denom <- survey.orgs.clean %>%
#   filter(!is.na(Q3.12_obstacle)) %>%
#   nrow()
# 
# df.plot.obstacles <- df.plot.obstacles.raw %>%
#   mutate(prop = num / df.plot.obstacles.denom) %>%
#   mutate(obstacle = capitalize(obstacle)) %>%
#   filter(num > 20, obstacle != "Other") %>%
#   mutate(obstacle = fct_inorder(obstacle))
# 
# plot.obstacles <- ggplot(df.plot.obstacles, aes(x=prop, y=fct_rev(obstacle))) +
#   geom_pointrangeh(aes(xmin=0, xmax=prop)) +
#   scale_x_continuous(labels=scales::percent) +
#   labs(x="Proportion of respondents", y=NULL) +
#   theme_ath() + theme(panel.grid.major.y=element_blank())
# 
# plot.obstacles
# 
# fig.save.cairo(plot.obstacles,
#                filename="3-obstacles",
#                width=4.5, height=2)
```

>>>>

---
title: "INGOs and instrumental factors"
format:
  html:
    code-fold: true
---

@@

```{r tab-activities-contentiousness-diffs}
#| tbl-cap: Median differences in proportion of high and low contention INGOs selecting frequency of type of work. Probability that the proportion is greater than 0 given in parentheses.
models_activities %>% 
  unnest(diffs_summary) %>% 
  mutate(nice_value = glue::glue(
    "{diff}<br>({p})",
    diff = label_number(style_negative = "minus", accuracy = 0.01)(y),
    p = label_number(accuracy = 0.01)(p_greater_0))
  ) %>% 
  ungroup() %>% 
  select(question, response, nice_value) %>% 
  pivot_wider(names_from = "response", values_from = "nice_value") %>% 
  gt() %>%
  fmt_markdown(columns = 2:4) %>%
  cols_align(align = "left", columns = question) %>%
  cols_label(question = "") %>% 
  tab_footnote(footnote = "Values show the differences in proportion of high and low contention INGOs providing each response (high contention proportion − low contention proportion)") %>% 
  opts_theme()
```

@@

```{r plot-obstacles, fig.width=6, fig.height=2}
df_obstacles_raw <- survey_orgs %>% 
  filter(!is.na(Q3.12_obstacle)) %>%
  mutate(obstacle = str_split(Q3.12_obstacle, ", ")) %>%
  unnest(obstacle) %>%
  mutate(obstacle = recode(obstacle,
                           `access to country` = "bureaucratic, legal, and political",
                           `political context` = "bureaucratic, legal, and political",
                           `bureaucratic and legal` = "bureaucratic, legal, and political"
  )) %>%
  group_by(obstacle) %>%
  summarise(num = n()) %>%
  arrange(desc(num))

df_obstacles_denom <- survey_orgs %>%
  filter(!is.na(Q3.12_obstacle)) %>%
  nrow()

df_obstacles <- df_obstacles_raw %>% 
  mutate(prop = num / df_obstacles_denom) %>% 
  mutate(obstacle = str_to_sentence(obstacle)) %>% 
  filter(num > 20, obstacle != "Other") %>%
  mutate(obstacle = fct_inorder(obstacle))

ggplot(df_obstacles, aes(x = prop, y = fct_rev(obstacle))) +
  geom_pointrange(aes(xmin = 0, xmax = prop)) +
  scale_x_continuous(labels = label_percent()) +
  labs(x = "Proportion of respondents", y = NULL) +
  theme_ingo() + 
  theme(panel.grid.major.y = element_blank())
```
